Vocabulary

### 2022-06-28 docs/02_vocabulary.Rmd
Add tests

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_futurama()(7),
	ggplot2.discrete.slab_color = ggsci::pal_futurama()(7),
	ggplot2.discrete.colour = ggsci::pal_futurama()(7)
)

@@

participants <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed")) %>% 
	filter(location=="Barcelona")
```

@@

```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(participant %in% fit_l1_4$data$participant) %>% 
	count(age_group, location)

sample_size_lp <- participants %>% 
	filter(
		participant %in% fit_l1_4$data$participant
	) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	geom_boxplot(
		aes(lp, vocab_size_l1, colour = is_imputed),
		position = position_dodge(width = 1),
		width = 0.25,
		size = 1
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = is_imputed),
		size = 1,
		alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(
			x = 1.5,
			y = 0, 
			label = paste0("N = ", n),
			group = lp
		),
		colour = "black",
		show.legend = FALSE, 
		position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", 
		colour = "Imputed", 
		fill = "Imputed",
		title = "L1 vocabulary size",
		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
	) +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.border = element_rect(fill = NA, colour = "grey", size = 1),
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(participant %in% fit_total_4$data$participant) %>% 
	count(age_group, location)

sample_size_lp <- participants %>% 
	filter(participant %in% fit_total_4$data$participant) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	geom_boxplot(
		aes(lp, vocab_size_l1, colour = is_imputed),
		position = position_dodge(width = 1),
		width = 0.25,
		size = 1
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = is_imputed),
		size = 1,
		alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(
			x = 1.5,
			y = 0, 
			label = paste0("N = ", n),
			group = lp
		),
		colour = "black",
		show.legend = FALSE, 
		position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (total)", colour = "Group", fill = "Group",
		title = "Total vocabulary size",
		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
	) +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_conceptual)) %>% 
	count(age_group, location)

sample_size_lp <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_total)) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
		geom_boxplot(
		aes(lp, vocab_size_l1, colour = is_imputed),
		position = position_dodge(width = 1),
		width = 0.25,
		size = 1
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = is_imputed),
		size = 1,
		alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(
			x = 1.5,
			y = 0, 
			label = paste0("N = ", n),
			group = lp
		),
		colour = "black",
		show.legend = FALSE, 
		position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "Conceptual vocabulary size",
		subtitle = "Percentage of lexicalised concepts reported to be understood from the vocabulary checklist"
	) +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_d3()(4),
	ggplot2.discrete.slab_color = ggsci::pal_d3()(4),
	ggplot2.discrete.colour = ggsci::pal_d3()(4)
)

@@

participants <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"))

@@

```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(participant %in% fit_3$data$participant) %>% 
	count(age_group)

sample_size_lp <- participants %>% 
	filter(
		participant %in% fit_3$data$participant
	) %>% 
	count(age_group, lp) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	aes(
		lp, 
		vocab_size_l1,
		colour = lp,
		fill = lp
	) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(
		aes(side = ifelse(lp=="Monolingual", "left", "right")),
		colour = "white",
		alpha = 0.5
	) +
	geom_boxplot(
		position = position_dodge(width = 1),
		width = 0.15,
		size = 1,
		colour = "black",
		fill = "white",
		outlier.colour = NA
	) +
	geom_point(
		aes(lp, vocab_size_l1),
		size = 2,
		shape = 1,
		stroke = 1,
		alpha = 0.75,
		position = position_jitterdodge(
			jitter.width = 0.8, 
			seed = 888, 
			dodge.width = 0.5
		)
	) +
	geom_text(
		data = sample_size_lp,
		aes(
			x = 1.5,
			y = 0, 
			label = paste0("N = ", n),
			group = lp
		),
		colour = "black",
		show.legend = FALSE, 
		position = position_dodge(width = 2),
		inherit.aes = FALSE
	) +
	labs(
		y = "Receptive vocabulary (L1)", 
		colour = "Imputed", 
		fill = "Imputed",
		title = "L1 vocabulary size",
		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
	) +
	scale_y_continuous(
		limits = c(0, 1),
		labels = percent
	) +
	theme_custom() +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	aes(
		lp, 
		vocab_size_total,
		colour = lp,
		fill = lp
	) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(
		aes(side = ifelse(lp=="Monolingual", "left", "right")),
		colour = "white",
		alpha = 0.5
	) +
	geom_boxplot(
		position = position_dodge(width = 1),
		width = 0.15,
		size = 1,
		colour = "black",
		fill = "white",
		outlier.colour = NA
	) +
	geom_point(
		aes(lp, vocab_size_total),
		size = 2,
		shape = 1,
		stroke = 1,
		alpha = 0.75,
		position = position_jitterdodge(
			jitter.width = 0.8, 
			seed = 888, 
			dodge.width = 0.5
		)
	) +
	geom_text(
		data = sample_size_lp,
		aes(
			x = 1.5,
			y = 0, 
			label = paste0("N = ", n),
			group = lp
		),
		colour = "black",
		show.legend = FALSE, 
		position = position_dodge(width = 2),
		inherit.aes = FALSE
	) +
	labs(
		y = "Receptive vocabulary (total)", colour = "Group", fill = "Group",
		title = "Total vocabulary size",
		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
	) +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme_custom() +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	aes(
		lp, 
		vocab_size_conceptual,
		colour = lp,
		fill = lp
	) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(
		aes(side = ifelse(lp=="Monolingual", "left", "right")),
		colour = "white",
		alpha = 0.5
	) +
	geom_boxplot(
		position = position_dodge(width = 1),
		width = 0.15,
		size = 1,
		colour = "black",
		fill = "white",
		outlier.colour = NA
	) +
	geom_point(
		aes(lp, vocab_size_conceptual),
		size = 2,
		shape = 1,
		stroke = 1,
		alpha = 0.75,
		position = position_jitterdodge(
			jitter.width = 0.8, 
			seed = 888, 
			dodge.width = 0.5
		)
	) +
	geom_text(
		data = sample_size_lp,
		aes(
			x = 1.5,
			y = 0, 
			label = paste0("N = ", n),
			group = lp
		),
		colour = "black",
		show.legend = FALSE, 
		position = position_dodge(width = 2),
		inherit.aes = FALSE
	) +
	labs(
		y = "Conceptual vocabulary", 
		x = "Group",
		fill = "Group",
		colour = "Group",
		title = "Conceptual vocabulary size",
		subtitle = "Percentage of lexicalised concepts reported to be understood from the vocabulary checklist"
	) +

	scale_y_continuous(
		limits = c(0, 1), 
		labels = percent
	) +
	theme_custom() +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

ggsave(here("img", "vocab_conceptual.png"))
